### 2018-03-12 paper/3-compute.tex
Move Identity monad to Appendix

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
dependencies :: Compute Applicative k v -> k -> [k]
dependencies compute = maybe [@@] getConst . compute (\k -> Const [k])
\end{minted}
\vspace{1mm}

@@

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
@\ghci@ dependencies add "A1"
[@@]
\end{minted}
\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
@\ghci@ dependencies add "B1"
["A1", "A2"]
\end{minted}
\vspace{1mm}

@@

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
newtype Const m a = Const { getConst :: m }
\end{minted}
\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
instance Functor (Const m) where
    fmap _ (Const m) = Const m
\end{minted}
\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
instance Monoid m => Applicative (Const m) where
    pure _              = Const mempty
    Const x <*> Const y = Const (x <> y)
\end{minted}
\vspace{1mm}

\noindent
A value of type \hs{Const}~\hs{[}\hs{k]}~\hs{v} contains no values \hs{v} but
allows us to record all invocations of the custom \hs{fetch} function that we
feed to the given compute: \hs{fetch k = Const [k]}. The compute returns a
value of type \hs{Maybe}~\hs{(Const}~\hs{[}\hs{k]}~\hs{v)}, which we can unwrap
using \hs{maybe [@@] getConst}, i.e. returning the empty list of dependencies
in case of an input.

We can also \hs{execute} a compute on a given store. This relies on a similar
transformation, now based on the \hs{Identity} monad and feeding
\hs{fetch k = pure (store k)} to the compute:

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
execute :: Compute Monad k v -> (k -> v) -> k -> Maybe v
execute compute store = fmap runIdentity . compute (pure . store)
\end{minted}
\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
newtype Identity a = Identity { runIdentity :: a }
\end{minted}
\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
instance Functor Identity where
    fmap f (Identity a) = Identity (f a)
\end{minted}
\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
instance Applicative Identity where
    pure a = Identity a
    Identity f <*> Identity a = Identity (f a)
\end{minted}
\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
instance Monad Identity where
    Identity a >>= f = f a
\end{minted}
\vspace{1mm}

@@

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
@\ghci@ store key = if key == "A1" then 10 else 20
@\ghci@ execute add store "A1"
Nothing
\end{minted}
\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
@\ghci@ execute add store "B1"
Just 30
\end{minted}
% \vspace{1mm}

@@

>>>>

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
import Data.Functor.Const
\end{minted}
\vspace{0.5mm}
\begin{minted}[xleftmargin=10pt]{haskell}
dependencies :: Compute Applicative k v -> k -> [k]
dependencies compute = maybe [@@] getConst . compute (\k -> Const [k])
\end{minted}
\vspace{1mm}

@@

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
@\ghci@ dependencies add "A1"
[@@]
\end{minted}
\begin{minted}[xleftmargin=10pt]{haskell}
@\ghci@ dependencies add "B1"
["A1", "A2"]
\end{minted}
\vspace{1mm}

@@

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
newtype Const m a = Const { getConst :: m }
\end{minted}
\vspace{0.5mm}
\begin{minted}[xleftmargin=10pt]{haskell}
instance Functor (Const m) where
    fmap _ (Const m) = Const m
\end{minted}
\vspace{0.5mm}
\begin{minted}[xleftmargin=10pt]{haskell}
instance Monoid m => Applicative (Const m) where
    pure _              = Const mempty
    Const x <*> Const y = Const (x <> y)
\end{minted}
\vspace{1mm}

\noindent
A value of type \hs{Const}~\hs{[}\hs{k]}~\hs{v} contains no values \hs{v} but
allows us to record all invocations of the custom \hs{fetch} function that we
feed to the given compute: \hs{fetch k = Const [k]}. The compute returns a
value of type \hs{Maybe}~\hs{(Const}~\hs{[}\hs{k]}~\hs{v)} that can be
unwrapped using \hs{maybe [@@] getConst}, i.e. returning the empty list of
dependencies in case of an input.

We can also \hs{execute} a compute on a given store. This relies on a similar
transformation, now based on the \hs{Identity} monad (see
Appendix~\S\ref{sec-appendix-transformers} for the implementation of
\hs{Identity}):

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
import Data.Functor.Identity
\end{minted}
\vspace{0.5mm}
\begin{minted}[xleftmargin=10pt]{haskell}
execute :: Compute Monad k v -> (k -> v) -> k -> Maybe v
execute compute store = fmap runIdentity . compute (pure . store)
\end{minted}
\vspace{1mm}

@@

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
@\ghci@ store key = if key == "A1" then 10 else 20
@\ghci@ execute add store "A1"
Nothing
\end{minted}
\begin{minted}[xleftmargin=10pt]{haskell}
@\ghci@ execute add store "B1"
Just 30
\end{minted}

@@

Now we need a combination of \hs{Const} and \hs{Identity}, which is the
\hs{Writer} monad!

### 2018-03-12 paper/9-appendix.tex
Move Identity monad to Appendix

\subsection{Compute examples}

>>>>

\subsection{Compute transformers}\label{sec-appendix-transformers}

In this section we clarify some of the compute transformers used in this paper.

\hs{execute} uses the transformation based on the \hs{Identity} monad, feeding
\hs{fetch k = pure (store k)} to the compute:

\begin{minted}[xleftmargin=10pt]{haskell}
execute :: Compute Monad k v -> (k -> v) -> k -> Maybe v
execute compute store = fmap runIdentity . compute (pure . store)
\end{minted}
\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
newtype Identity a = Identity { runIdentity :: a }
\end{minted}
\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
instance Functor Identity where
    fmap f (Identity a) = Identity (f a)
\end{minted}
\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
instance Applicative Identity where
    pure a = Identity a
    Identity f <*> Identity a = Identity (f a)
\end{minted}
\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
instance Monad Identity where
    Identity a >>= f = f a
\end{minted}
\vspace{1mm}

\todo{AM}{Explain \hs{trackDependencies}.}

\subsection{Compute examples}\label{sec-appendix-compute-examples}

\todo{AM}{Add some explanatory text.}
